---
title: "task_switching_analysis"
authors: "Seunghwan (Nigel) Kim, Sunny Lou"
date: "1/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup and load data
required libraries: dplyr, tidyr, ggplot2, ggpubr, lmerTest, lubridate
```{r lib, results='hide', error=FALSE, warning=FALSE, message=FALSE}
# install.packages('ggpubr')
# install.packages('lmerTest')
# install.packages('lubridate')
# install.packages('tidyr')

library(dplyr)
library(ggplot2)
library(ggpubr)
library(lmerTest)
library(lubridate)
library(tidyr)
```

## Generate Table 1
Basic user measurements (median(IQR))

```{r table1}
df_phys = read.csv('./result/user_measurements_ICUattendings_physicians_anesthesiologists_01252022.csv')
df_np_pa = read.csv('./result/user_measurements_NP_PA_shifts_01252022.csv')

# Attending physicians

# imputing NAs to 0 for two columns (Valid. Python code should have been filling these with 0 but it was written in a way that it filled them with NA)
df_phys$num_pts_w_notes[is.na(df_phys$num_pts_w_notes)] <- 0
df_phys$num_pts_w_orders[is.na(df_phys$num_pts_w_orders)] <- 0

dim(df_phys)
df_phys = df_phys[(df_phys$num_actions != 0), ] #decided to use

df_phys %>%
  select(total_ehr_time, afterhours_ehr_time, num_pts_viewed, num_actions,
         num_messages, inbox_time, num_orders, order_time, num_note, time_note, 
         review_time, num_pts_w_notes, num_pts_w_orders, tot_switches, tot_sessions,
         avg_session_duration, avg_switch_per_session, switch_rate_100, 
         avg_timedelta_switches, switches_per_minute_session,
         switches_per_hour_ehr_time) %>%
  summary()


# APPs

df_np_pa$num_pts_w_notes[is.na(df_np_pa$num_pts_w_notes)] <- 0
df_np_pa$num_pts_w_orders[is.na(df_np_pa$num_pts_w_orders)] <- 0

dim(df_np_pa)
df_np_pa = df_np_pa[(df_np_pa$num_actions != 0), ]
dim(df_np_pa)

df_np_pa %>%
  select(total_ehr_time, afterhours_ehr_time, num_pts_viewed, num_actions,
         num_messages, inbox_time, num_orders, order_time, num_note, time_note, 
         review_time, num_pts_w_notes, num_pts_w_orders, tot_switches, tot_sessions,
         avg_session_duration, avg_switch_per_session, switch_rate_100, 
         avg_timedelta_switches, switches_per_minute_session,
         switches_per_hour_ehr_time) %>%
  summary()
```
## Task switching and Total EHR time
linear mixed effects model
- target: total_ehr_time
- fixed effect: switch rate, gender, patient load
- random effect: individual

```{r physicians}
m1_phys = lmer(total_ehr_time ~ 
                 switch_rate_100+Gender+num_pts_w_notes+(1|USER_ID), df_phys)

summary(m1_phys)
confint(m1_phys)

```

```{r APPs}
# models
m1_np_pa = lmer(total_ehr_time ~ 
                 switch_rate_100+Gender+num_pts_w_notes+(1|USER_ID), df_np_pa)

summary(m1_np_pa)
confint(m1_np_pa)
```

### Scale coefficients using interquartile range (IQR)
Example: For a 1st to 3rd quartile increase in switch rate per 100 actions (i.e., from 4.027 to 8.579 switches per 100 actions), the total time spent on EHR increases by 25% (RR=1.25, 95% CI 1.03-1.47).

```{r coeffs scaled by iqr}
scale_coefs_by_iqr = function(m, vars, df, ci_method = 'profile') {
  # m - saved model object
  # vars - list of string variable names in m, in alphabetical order
  # df - data table containing the data used for the model
  # ci_method - "profile" to calculate profile confidence intervals, wald otherwise
  betas = fixef(m) 
  if (ci_method == 'profile') {
    cis = confint(m)
  } else {
    cis = confint.default(m)
  }
  betas = betas[vars]

  lower_ci = cis[vars, 1]
  upper_ci = cis[vars, 2]

  
  iqrs = rstatix::get_summary_stats(df[vars], type='median_iqr')
  iqrs
  iqrs = iqrs %>%
    mutate(
      beta_scaled = iqr*betas,
      lower = iqr*lower_ci,
      upper = iqr*upper_ci
           )
  iqrs
  return(iqrs)
}
```

``` {r switch rate per 100}
# Switch rate per 100 actions

m_app = m1_np_pa # m1_phys
m_phys = m1_phys

vars = c('num_pts_w_notes', 'switch_rate_100') # alphabetical order

iqrs_app = scale_coefs_by_iqr(m_app, vars, df_np_pa)
iqrs_app
iqrs_phys = scale_coefs_by_iqr(m_phys, vars, df_phys)
iqrs_phys

```

## Wrong patient analysis

### Advanced practice provider RAR statistics

```{r}
df = read.csv('./result/user_measurements_NP_PA_shifts_01252022.csv') %>%
  mutate(
    switch_rate_hour = tot_switches/total_ehr_time
  ) %>%
  filter(num_actions > 0)

# head(df)
```

```{r}
df %>% # distribution of num RAR events per day per provider
  count(RAR_count)

df %>% # some providers make more errors than others
  group_by(USER_ID) %>%
  summarize(num_errors_tot = sum(RAR_count),
            num_shifts = n(),
            errors_per_shift = num_errors_tot/num_shifts
            ) %>%
  ggplot(aes(errors_per_shift)) + geom_histogram() + 
    ylab('count of providers') + xlab('mean RAR events per shift by provider')

# df %>% # num shifts per provider
#   count(USER_ID)
# 
# sum(df$num_actions)
```

### RAR analysis normalized by number of EHR actions

**Interpretation:** The relationship between switch rate normalized per 100 EHR actions and RAR events is shown below. For a 1st to 3rd quartile increase in switch rate per 100 actions (i.e., from 4.027 to 8.579 switches per 100 actions), the rate of RAR events increases by 28% (RR=1.28, 95% CI 1.04-1.55).

```{r}
df_ = df %>% filter(num_orders > 0) # remove shifts were no orders were placed
 
rar_model = glm(RAR_count ~ switch_rate_100 + num_pts_w_notes
                + offset(log(num_orders)),
                family = "poisson", data = df_)
summary(rar_model)
exp(cbind(rate_ratio=coef(rar_model), confint(rar_model)))
summary(df$switch_rate_100)
```

```{r coeffs scaled by iqr}
scale_coefs_by_iqr = function(m, vars, df, ci_method = 'profile') {
  # m - saved model object
  # vars - list of string variable names in m, in alphabetical order
  # df - data table containing the data used for the model
  # ci_method - "profile" to calculate profile confidence intervals, wald otherwise
  betas = coef(m) 
  if (ci_method == 'profile') {
    cis = confint(m)
  } else {
    cis = confint.default(m)
  }
  betas = betas[vars]
  lower_ci = cis[vars, 1]
  upper_ci = cis[vars, 2]
  
  iqrs = rstatix::get_summary_stats(df[vars], type='median_iqr')
  iqrs = iqrs %>%
    mutate(
      beta_scaled = iqr*betas,
      lower = iqr*lower_ci,
      upper = iqr*upper_ci
           )
  return(iqrs)
}

m = rar_model
vars = c('num_pts_w_notes', 'switch_rate_100') # alphabetical order
# iqrs = scale_coefs_by_iqr(m, vars, df_)
iqrs = scale_coefs_by_iqr(m, vars, df)

# exponentiated beta coefficients
iqrs %>%
  mutate(
    rate_ratio = exp(beta_scaled),
    lower = exp(lower),
    upper = exp(upper)
  ) %>%
  select(variable, rate_ratio, lower, upper, median, iqr)
```
